Multi-channel Kondo model URG

### 2021-11-30 notes/multi-channel-urg.tex
errors in the eigenvalue of pi^z

Defining \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
\begin{equation}\begin{aligned}
	H_m = \begin{pmatrix} \frac{Jm}{2} & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\frac{J}{2}(m+1) \end{pmatrix} , m \in \left[-M, M-1\right] 
\end{aligned}\end{equation}
The eigenvalues are 
\begin{equation}\begin{aligned}
	% \label{eigenvalue}
	\lambda_{\pm}^{M} = - \frac{J}{4} \pm \frac{J}{2}\left(M + \frac{1}{2}\right) 
\end{aligned}\end{equation}
The eigenvalues of the terminal states are \(\frac{JM}{2}\). The set of eigenvalues \(\lambda^{M_\text{max}}_-\) form the ground state subspace \(\left\{ \ket{\Psi^M_{m,-}} \right\} \) of degeneracy \(2M_\text{max} = K\). This common \(K-\)fold degenerate eigenvalue is \(-\frac{J}{2}(M+1)\).
The eigenstates for each value of \(M,m\) for the \(2\times 2\) blocks are given by
\begin{equation}\begin{aligned}
	\ket{\Psi^M_{m,-}} &= -\sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M + m + 1\right)\ket{\downarrow,M,m+1},& m \in \left[-M, M-1\right] \\
	\ket{\Psi^M_{m,+}} &= \sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M - m\right)\ket{\downarrow,M,m+1},& m \in \left[-M, M-1\right]
\end{aligned}\end{equation}
Note that we are using the index \(m\) simplify to indicate the subsapce from which these eigenstates arise; \(m\) is not a quantum number for that eigenstate. The eigenvalue of \(\pi^z\) is, however, a quantum number. We have the eigenvalue relation \(\pi^z \ket{S_d^z} = (-1)^{2\left(S_d^z + m\right)}\). Applying \(\pi^z\) on these eigenstates gives
\begin{equation}\begin{aligned}
	\pi^z\ket{\Psi^M_{m,-}} = -\left( -1 \right)^{2(1/2 + m)}\sqrt{x_m^M}\ket{\uparrow, M, m} + \left( -1 \right)^{2(-1/2 + m + 1)}\left(M + m + 1\right)\ket{\downarrow,M,m+1} = \left( -1 \right) ^{2m+1}\ket{\Psi^M_{m,-}}
\end{aligned}\end{equation}
This shows that the operator \(\pi^z\) splits the \(K-\)fold degenerate ground state manifold into two sub-manifolds of \(\pi^z\) parity \(\pm 1\).

It is interesting to calculate the action of the parity operator \(\pi^x\) on these eigenstates. We can write that operator as
\begin{equation}\begin{aligned}
	\pi^x = (S_d^+ + S_d^-)\otimes_{i=1}^K \left(s_i^+ + s_i^-\right) 
\end{aligned}\end{equation}
We can write the eigenstates of \(s_\text{tot}^z\) in terms of the eigenstates of \(s_i^z\) using their Clebsh-Gordon coefficients:
\begin{equation}\begin{aligned}
	\ket{M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}\ket{m_1,m_2,...,m_K} C_{\left\{m_i\right\},m,M}
\end{aligned}\end{equation}
where \(C_{\left\{m_i\right\},m,M} = \braket{m_1,m_2,...,m_K|m,M}\) are the Clebsh-Gordon coefficients. Applying the parity operator on the state gives
\begin{equation}\begin{aligned}
	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}(S_d^+ + S_d^-)\ket{S_d^z}\otimes_{i=1}^K \left(s_i^+ + s_i^-\right)\ket{m_i} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{-m_i}\\
	=\sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{-m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i}
\end{aligned}\end{equation}
Using the identity \(\braket{M_1m_1,M_2m_2,\ldots|m,M} = \left( -1 \right)^{\sum_i M_i - M}\braket{M_1, -m_1; M_2 -m_2;\ldots|-m,M}\), we have \(C_{\left\{-m_i\right\},m,M} = C_{\left\{m_i\right\},-m,M}\). Substituting this, we get
\begin{equation}\begin{aligned}
	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{m_i\right\},-m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i} = \ket{-S_d^z, M, -m}
\end{aligned}\end{equation}
The action of \(\pi^x\) on the eigenstates can now be determined:
\begin{equation}\begin{aligned}
	\pi^x \ket{\Psi^M_{m,-}} &=-\sqrt{x_m^M}\ket{\downarrow, M, -m} + \left(M + m + 1\right)\ket{\uparrow,M,-m-1} = \ket{\Psi^M_{-m-1,-}}
\end{aligned}\end{equation}
The last equality holds up to a minus sign. It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvalues. In other words, \(\pi^x\) connects the two sectors of opposite \(\pi^z\) parity.

>>>>

Defining \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
\begin{equation}\begin{aligned}
	H_m = \begin{pmatrix} \frac{Jm}{2} & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\frac{J}{2}(m+1) \end{pmatrix} , m \in \left[-M, M-1\right] 
\end{aligned}\end{equation}
The eigenvalues are 
\begin{equation}\begin{aligned}
	% \label{eigenvalue}
	\lambda_{\pm}^{M} = - \frac{J}{4} \pm \frac{J}{2}\left(M + \frac{1}{2}\right) 
\end{aligned}\end{equation}
The eigenvalues of the terminal states are \(\frac{JM}{2}\). The set of eigenvalues \(\lambda^{M_\text{max}}_-\) form the ground state subspace \(\left\{ \ket{\Psi^M_{m,-}} \right\} \) of degeneracy \(2M_\text{max} = K\). This common \(K-\)fold degenerate eigenvalue is \(-\frac{J}{2}(M+1)\).
The eigenstates for each value of \(M,m\) for the \(2\times 2\) blocks are given by
\begin{equation}\begin{aligned}
	\ket{\Psi^M_{m,-}} &= -\sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M + m + 1\right)\ket{\downarrow,M,m+1},& m \in \left[-M, M-1\right] \\
	\ket{\Psi^M_{m,+}} &= \sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M - m\right)\ket{\downarrow,M,m+1},& m \in \left[-M, M-1\right]
\end{aligned}\end{equation}
Note that we are using the index \(m\) to indicate the subspace from which these eigenstates arise; \(m\) is not a quantum number for that eigenstate. The eigenvalue of \(\pi^z\) is, however, a quantum number. We have the eigenvalue relation \(\pi^z \ket{S_d^z} = (-1)^{\frac{1}{2}\left(\sigma^z_d + 2m - 1\right)}\). Applying \(\pi^z\) on these eigenstates gives
\begin{equation}\begin{aligned}
	\pi^z\ket{\Psi^M_{m,-}} = -\left(-1\right)^{\frac{1 + 2m - 1}{2}}\sqrt{x_m^M}\ket{\uparrow, M, m} + \left( -1 \right)^{\frac{-1 + 2m + 2 - 1}{2}}\left(M + m + 1\right)\ket{\downarrow,M,m+1} = \left( -1 \right) ^{m}\ket{\Psi^M_{m,-}}
\end{aligned}\end{equation}
This shows that the operator \(\pi^z\) splits the \(K-\)fold degenerate ground state manifold into two sub-manifolds of \(\pi^z\) parity \(\pm 1\). The odd values of \(m\) form the negative parity sector \(\pi^z = -1\) while the even values form the positive parity sector \(\pi^z = 1\).

It is interesting to calculate the action of the parity operator \(\pi^x\) on these eigenstates. We can write that operator as
\begin{equation}\begin{aligned}
	\pi^x = (S_d^+ + S_d^-)\otimes_{i=1}^K \left(s_i^+ + s_i^-\right) 
\end{aligned}\end{equation}
We can write the eigenstates of \(s_\text{tot}^z\) in terms of the eigenstates of \(s_i^z\) using their Clebsch-Gordon coefficients:
\begin{equation}\begin{aligned}
	\ket{M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}\ket{m_1,m_2,...,m_K} C_{\left\{m_i\right\},m,M}
\end{aligned}\end{equation}
where \(C_{\left\{m_i\right\},m,M} = \braket{m_1,m_2,...,m_K|m,M}\) are the Clebsch-Gordon coefficients. Applying the parity operator on the state gives
\begin{equation}\begin{aligned}
	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}(S_d^+ + S_d^-)\ket{S_d^z}\otimes_{i=1}^K \left(s_i^+ + s_i^-\right)\ket{m_i} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{-m_i}\\
	=\sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{-m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i}
\end{aligned}\end{equation}
Using the identity \(\braket{M_1m_1,M_2m_2,\ldots|m,M} = \left( -1 \right)^{\sum_i M_i - M}\braket{M_1, -m_1; M_2 -m_2;\ldots|-m,M}\), we have \(C_{\left\{-m_i\right\},m,M} = C_{\left\{m_i\right\},-m,M}\). Substituting this, we get
\begin{equation}\begin{aligned}
	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{m_i\right\},-m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i} = \ket{-S_d^z, M, -m}
\end{aligned}\end{equation}
The action of \(\pi^x\) on the eigenstates can now be determined:
\begin{equation}\begin{aligned}
	\pi^x \ket{\Psi^M_{m,-}} &=-\sqrt{x_m^M}\ket{\downarrow, M, -m} + \left(M + m + 1\right)\ket{\uparrow,M,-m-1} = \ket{\Psi^M_{-m-1,-}}
\end{aligned}\end{equation}
The last equality holds up to a minus sign. It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvalues. In other words, \(\pi^x\) connects the two sectors of opposite \(\pi^z\) parity:
\begin{equation}\begin{aligned}
	\pi^x \ket{(-1)^m} = \ket{(-1)^{-1-m}} = \ket{-(-1)^m}
\end{aligned}\end{equation}
